The K2 Bright Star Survey

### 2019-05-31 paper/ms.tex
guniibuu is 36 oph in gamilaraay

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations. Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision lightcurves.

@@

% briefly intro the halo method and halo literature
In order to recover precise light curves of the brightest stars in \ktwo, we have therefore developed two main approaches, `smear' and `halo' photometry. Smear photometry \citep{Pope2016,smearcampaign} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. This can be processed recover light curves of stars that were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns. The main disadvantage of this method is that it confuses all stars in the same column, which means that in crowded fields smear light curves tend to be significantly contaminated.

@@

% describe contents of paper: code, catalog, categorization, conclusions
In this Paper we describe numerical experiments testing the TV-min method and extending it to generalizations with different exponents and timescales. We show that the method as previously employed applying standard TV-min is suboptimal, and gain a modest improvement from taking finite differences close to the timescale of \ktwo thruster firings. We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases. 
We go on to present complete catalog of long-cadence \ktwo halo light curves, which we have made publicly available. We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability. These include oscillating red giants, pulsating and quiet main-sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry. We hope that this diverse catalog of light curves will be useful for a range of astrophysical investigations.

@@

This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}. $Q_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution. In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.

@@

In order to choose the values for $k$ and $\delta$ in our objective function, we used the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the sample of stars with halo apertures, and one with very little high frequency variability detected or predicted. It was also observed at short cadence. We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better.

We calculated halo lightcurves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data. The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}. We found that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP. This is unsurprising: that this is one cadence shorter than the 12~cadence thruster firing period. In this context we can understand the optimum as suppressing systematics on the same timescale as they occur. On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.

@@

We want to compare the photometric precision obtained to that from SAP and normal calibration pipelines, and ascertain whether we systematically distort the scale of variation or the power spectrum of variability. In order to do this, we take the sample of stars with $11.5 <  Kp < 12.5$ from \ktwo Campaign~6, for which \textsc{k2sc} light curves are available, choosing~2466 stars that are as bright as possible without saturation. The planets in this campaign are well characterized \citep[e.g.][]{Pope2016planets}, and eight singly-transiting systems are known in this magnitude range. We take the entire target pixel file without using any aperture restriction, and run TV-min with $\delta = 10$ for each of these planets and compare these to light curves from the PDC pipeline. In both cases, we correct residual systematics with \textsc{k2sc}, prewhiten with the GP time trend model, clip $3\,\sigma$ upwards outliers, and normalize the final fluxes to unity. These are then folded on the known transit period and zero epoch as tabulated in the NASA Exoplanet Archive \citep{2013PASP..125..989A}, and the folded lightcurves are binned in 3-cadence bins to reduce white noise in the comparison. The results are displayed in Figure~\ref{fig:planets}.

@@

We now seek to establish the global noise properties of the whole unsaturated sample, and compare these to PDC. We process all~2466 stars with TV-min and $\delta = 10$, using all pixels in the TPF unmasked. Because these stars are so bright and the TPFs so small, in the great majority  of cases we do not expect significant contamination, and this is a way of testing how well the weights assigned by TV-min match the flux distribution over pixels. For each lightcurve we calculated the 6.5\,hr CDPP proxy with \texttt{lightkurve} as a measure of SNR, and we plot the results of the two pipelines against one another in Figure~\ref{fig:halovspdc}. We see that a significant number of stars have high PDC CDPP but low TV-min CDPP, which raises the possibility that these are variables for which halo is overcorrecting. We found by inspection of the weightmaps and \kepler pipeline aperture masks that these mostly consist of stars for which the SAP aperture is significantly smaller than the PSF. In this case, by ignoring the pipeline apertures, \texttt{halophot} is in fact generating significantly better light curves. Over all stars, we found that the fractional enclosed halo weight in the \kepler pipeline aperture is only $0.19 \pm 0.11$, which suggests that in fact the apertures are systematically smaller than optimal for stars of this magnitude, and that TV-min is using information in the fainter pixels to help correct systematics.

@@

Histograms of the CDPPs of the SAP, PDC and halo light curves with and without \textsc{k2sc} are displayed in Figure~\ref{fig:cdpphists}. We see that both halo and PDC significantly outperform SAP, with halo performing better than PDC with no additional correction. Nevertheless, after \textsc{k2sc}, we found that the best PDC lightcurves have a smaller CDPP than the best similarly pointing-corrected halo. We conjecture that PDC with its improved calibration for common-mode systematics and blended/background light is correcting for effects that halo, as a single-star and instrument-agnostic method, does not.

@@

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were assigned short-cadence halo apertures. For these targets we have provided both long- and short-cadence reductions. Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and on choice of objective function, and for consistency with long cadence, we have adopted a 300~cadence lag (i.e. $30 \times$ the long cadence lag of 10) and the L1 TV objective function. With their many time samples, the short-cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo lightcurves.

>>>>

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations. Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision light curves.

@@

% briefly intro the halo method and halo literature
In order to recover precise light curves of the brightest stars in \ktwo, we have therefore developed two main approaches, `smear' and `halo' photometry. Smear photometry \citep{Pope2016,smearcampaign} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. This can be processed to recover light curves of stars that were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns. The main disadvantage of this method is that it confuses all stars in the same column, which means that in crowded fields smear light curves tend to be significantly contaminated.

@@

% describe contents of paper: code, catalog, categorization, conclusions
In this Paper we describe numerical experiments testing the TV-min method and extending it to generalizations with different exponents and timescales. We show that the method as previously employed applying standard TV-min is suboptimal, and gain a modest improvement from taking finite differences close to the timescale of \ktwo thruster firings. We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases. 
We go on to present a complete catalog of long-cadence \ktwo halo light curves, which we have made publicly available. We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability. These include oscillating red giants, pulsating and quiet main-sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with high-cadence space photometry. We are convinced that this diverse catalog of high-precision light curves will be useful for a range of astrophysical investigations.

@@

This is a classic convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}. $Q_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution. In practice, for computational reasons we optimize over parameters $\tilde{w}_j$ such that $w_j = \text{softmax}(\tilde{w}_j)$, as this satisfies the constraint that $\forall_j w_j > 0$, and while this also constrains their sum to be unity, we renormalize $f$ to satisfy its normalization constraint before calculating the objective function and this additional constraint is removed again.

@@

In order to choose the values for $k$ and $\delta$ in our objective function, we used the quiet system 36~Ophiuchi (Guniibuu, $V= 5.08$), a K1/K2/K5 main sequence triple system consisting of the lowest-mass main sequence stars in the sample of stars with halo apertures. Very little high frequency variability is detected or predicted. It was also observed at short cadence. We chose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a light curve, with lower being better.

We calculated halo light curves of 36\,Oph and their CDPPs for $k \in \{1,2,3\}$, and $\delta \in [1,50]$ for long cadence and for various valies of $\delta \in [1,2500]$ for short cadence data. The results are displayed in Figures~\ref{cdpps_lc} and~\ref{cdpps_sc}. We found that for long cadence data, $k=1$ (TV) and a lag $\delta=10$ provide the best CDPP. This is unsurprising: that this is one cadence shorter than the 12~cadence thruster firing period. In this context we can understand the optimum as suppressing systematics on the same timescale as they occur. On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ with slow improvement with larger $\delta$, and performs very poorly for $k=3$ at all lags.

@@

We want to compare the photometric precision obtained to that from SAP and normal calibration pipelines, and ascertain whether we systematically distort the scale of variation or the power spectrum of variability. In order to do this, we take the sample of stars with $11.5 <  Kp < 12.5$ from \ktwo Campaign~6, for which \textsc{k2sc} light curves are available, choosing~2466 stars that are as bright as possible without saturation. The planets in this campaign are well characterized \citep[e.g.][]{Pope2016planets}, and eight singly-transiting systems are known in this magnitude range. We take the entire target pixel file without using any aperture restriction, and run TV-min with $\delta = 10$ for each of these planets and compare these to light curves from the PDC pipeline. In both cases, we correct residual systematics with \textsc{k2sc}, prewhiten with the GP time trend model, clip $3\,\sigma$ upwards outliers, and normalize the final fluxes to unity. These are then folded on the known transit period and zero epoch as tabulated in the NASA Exoplanet Archive \citep{2013PASP..125..989A}, and the folded light curves are binned in 3-cadence bins to reduce white noise in the comparison. The results are displayed in Figure~\ref{fig:planets}.

@@

We now seek to establish the global noise properties of the whole unsaturated sample, and compare these to PDC. We process all~2466 stars with TV-min and $\delta = 10$, using all pixels in the TPF unmasked. Because these stars are so bright and the TPFs so small, in the great majority  of cases we do not expect significant contamination, and this is a way of testing how well the weights assigned by TV-min match the flux distribution over pixels. For each light curve we calculated the 6.5\,hr CDPP proxy with \texttt{lightkurve} as a measure of SNR, and we plot the results of the two pipelines against one another in Figure~\ref{fig:halovspdc}. We see that a significant number of stars have high PDC CDPP but low TV-min CDPP, which raises the possibility that these are variables for which halo is overcorrecting. We found by inspection of the weightmaps and \kepler pipeline aperture masks that these mostly consist of stars for which the SAP aperture is significantly smaller than the PSF. In this case, by ignoring the pipeline apertures, \texttt{halophot} is in fact generating significantly better light curves. Over all stars, we found that the fractional enclosed halo weight in the \kepler pipeline aperture is only $0.19 \pm 0.11$, which suggests that in fact the apertures are systematically smaller than optimal for stars of this magnitude, and that TV-min is using information in the fainter pixels to help correct systematics.

@@

Histograms of the CDPPs of the SAP, PDC and halo light curves with and without \textsc{k2sc} are displayed in Figure~\ref{fig:cdpphists}. We see that both halo and PDC significantly outperform SAP, with halo performing better than PDC with no additional correction. Nevertheless, after \textsc{k2sc}, we found that the best PDC light curves have a smaller CDPP than the best similarly pointing-corrected halo. We conjecture that PDC with its improved calibration for common-mode systematics and blended/background light is correcting for effects that halo, as a single-star and instrument-agnostic method, does not.

@@

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were assigned short-cadence halo apertures. For these targets we have provided both long- and short-cadence reductions. Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and on choice of objective function, and for consistency with long cadence, we have adopted a 300~cadence lag (i.e. $30 \times$ the long cadence lag of 10) and the L1 TV objective function. With their many time samples, the short-cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo light curves.
